\acknowledgements{	\OnePageChapter	% *MUST* BE ONLY ONE PAGE!
	This journey would not have been possible without the support of my family, advisor, and friends.
	I would like to express my gratitude to my parents and my family.
	They are my biggest supporters.
	Thank you to my parents Ahmed and Nora who always believed in me and encouraged me to pursue my dreams.
	I'm grateful to my wife Zaynab, who always provided me with support and kept me happy.
	
	There are a number of people who made this work possible but at the top of this list is my PhD advisor, Tom Yeh, who took me as his first PhD student, taught me how to write a research paper, carefully reviewed my code and design choices, and helped me with organizing my talks.
	His keen advice helped me identify research directions and come up with new approaches to problems.
	He got me involved in the publication process early on, encouraged me to submit my early work as works-in-progress, and assigned me as reviewer in top conferences in my area.
	I recall the difficulties I encountered in my first year and how harsh and hypercritical academia felt.
	Tom taught me how to deal with it in a positive way.
	I'm extremely lucky and grateful that I worked with him.
	
	I would like to thank the members of my committee: Danielle Szafir, Shaun Kane, Kenneth Anderson, and Qin Lv.
	I would also like to thank Jackson Chen, without him the size of our dataset would be much smaller, and Sanghee Kim who helped me with setting up the RAID and the infrastructure to run the early stage of my research.
	I would like to express my appreciation to all my colleagues at the Sikuli lab.
	Finally, I would like to thank King Abdulaziz University, which helped fund my research through a generous scholarship program, and thank Amazon for their AWS Cloud Credits for Research program, which helped cover my computing costs.
	}
